---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dataeditfjp

<!-- badges: start -->
<!-- badges: end -->

The dataeditfjp package aims to facilitate data manipulation, analysis, and report generation, with a focus on applications related to data editing. It was developed to support researchers and analysts at the João Pinheiro Foundation (FJP) and the broader community.

## Installation

You can install the development version of **dataeditfjp** from [GitHub](https://github.com/) with:

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("FundacaoJoaoPinheiro/dataeditfjp@development")
```

## Usage Example

Here is a basic example showing how to use the package to generate a report:

```{r example, eval=FALSE}
## basic example code
library(dataeditfjp)
dataeditfjp::create_report()
```

## Funding

This study was developed with financial support from the Research Support Foundation of the State of Minas Gerais (Fapemig) under the project "Building Capacities and Expanding Frontiers in Research at FJP" - Call No. 003/2023.

## Team

* Coordination Social Indicators: Ester Carneiro C. Santos
* Unit of Statistics and Data Management: Renato Vale
* Script Development: Erick C. Amorim, Igor Souza and Luiz Pataca.

## Contributions

Contributions are welcome! If you wish to contribute to the development of this package, please open an issue or a pull request on the GitHub repository or contact us at: [dados@fjp.mg.gov.br]()
